### 2017-06-05 sheets/talk-6/sheet-6.tex
Add hint on sheet 6 that "We will now assume that all the 6 constructions are unique up-to isomorphism."
Solution for 6: Minus-Core

@@

\begin{definition}{Minus-Core of Vector Spaces}
  Let $V, W$ be Vector Spaces over a field $K$. Let $s, t \from V \to W$ be linear functions.
  We define the linear function $s - t := \lambda v\in V. \; v(s) - t(s)$.
  Remember the definition $\forall g \from V \to W: core(g) := \set{ v \in V | g(v) = 0 }$.
  Now $core (s - t) = \set{v \in V | s(v) = t (v) }$.
\end{definition}

@@

>>>>

\hint{We will now assume that all the 6 constructions are unique up-to isomorphism.}

@@

\begin{definition}{Minus-Core of Linear Maps in Vector Spaces}
  Let $V, W$ be Vector Spaces over a field $K$. Let $s, t \from V \to W$ be linear functions.
  We define the linear function $s - t := \lambda v\in V. \; v(s) - t(s)$.
  Remember the definition $\forall g \from V \to W: core(g) := \set{ v \in V | g(v) = 0 }$.
  Now $core (s - t) = \set{v \in V | s(v) = t (v) }$.
\end{definition}

@@

\begin{answer}
  \begin{proof}
    Let $i \from core(s-t) \to X$ be a inclusion function. Let
    $\xymatrix{
      A \ar[r]^f & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
    }$
    be a commuting diagramm. Note that $f A \subseteq core(s-t)$.
    Thus we can define $\bar{f} \from A \to core(s-t)$ with $\bar{f}(a) := f(a)$.
    We see that $\forall a \in A: i(\bar{f}(a))=\bar{f}(a)=f(a)$, thus $i \of \bar{f} = f$.
    Let $\tilde{f} \from A \to core(s-t)$ be another map such that $i \of \tilde{f} = f$.
    Now $\tilde{f}(a) = i(\tilde{f}(a)) = i(\bar{f}(a)) = \bar{f}(a)$.
  \end{proof}
\end{answer}
